\cvsection{Experience}
\begin{cventries}
    %---------------------------------------------------------
    \cventry
    {Head of Windows servers engineering} % Position
    {Société Générale} % Company
    {Paris, France} % Location
    {May 2014 - Sept. 2015} % Date(s)
    { % Description
        Manage a team of 8 people which main missions were: \hfill\break
        \begin{cvitems}
            \item {Develop and maintain transversal tools to secure administration of around 10K Windows servers distributed in 15 countries}
            \item {Leverage and integrate new hardware and software}
            \item {Deliver expertise and level 4 support to system administrators}
            \item {Standardize and automate as much processes as possible}
        \end{cvitems} \hfill\break
        Some key deliverables were: \hfill\break
        \begin{cvitems}
            \item {Transversal applications migration / SCCM, Symantec EP /}
            \item {Set of tools to automate compliance to standard detection, result storage and automatic reports generation / DCM, PowerShell, GIT, REST API, SCCM, WMI /}
            \item {Automate administration tasks such as OS deployment, filesystem extension, accounts provisioning. / HPOO, REST API, GIT, Bootstrap /}
            \item {Create a SCDB for Windows assets retrieving data from various sources and aggregating them / MSSQL, SSIS, PowerShell, GIT /}
            \item {Build procedures and tools to assist internal clients during their migration from Windows 2003}
            \item {Migration of the legacy Active Directory 2003 architecture to 2008R2}
            \item {Migration of around 30 software source codes under GIT versioning system with unit testing and continuous integration}
        \end{cvitems} \hfill\break
        \begin{cvskills}
            \cvskill {Technical context} {Windows 2003, Windows 2008 R2, Windows 2012, VMWare}
            \cvskill {Functional skills} {team management, capacity planning, demand management, agile management}
        \end{cvskills}
    }
    %---------------------------------------------------------

    %---------------------------------------------------------
    \cventry
    {Security team leader} % Position
    {Société Générale} % Company
    {Paris, France} % Location
    {Jul. 2011 - Sept. 2014} % Date(s)
    { % Description
        Within a team of 80 people, administrating 20K systems (Unix and Windows), my main missions were: \hfill\break
        \begin{cvitems}
            \item {Be the security point of contact}
            \item {Manage a 380K€/year project portfolio}
            \item {Manage around 7 people (2 direct report)}
            \item {Build and maintain tools to enhance security efficiency}
            \item {Innovate to be proactive on threats and detection behavior}
            \item {Provide technical expertise to harden systems and help on forensic analysis}
        \end{cvitems} \hfill\break
        Some key deliverables were: \hfill\break
        \begin{cvitems}
            \item {Application to allow a more agile management of accounts, accesses and rights for end-users through REST APIs providing a standardized abstraction layer to complex tools and procedures of Unix and Windows systems. / Python, Django, REST API, MySQL, OAuth2, Centrify, Active Directory, KSH /}
        \end{cvitems} \hfill\break
        \begin{cvskills}
            \cvskill {Technical context} {Windows Server 2003 \& 2008R2, Solaris 9 \& 10, Red Hat EL 5 \& 6}
            \cvskill {Functional skills} {project management, agile methods, small team management}
        \end{cvskills}
    }
    %---------------------------------------------------------

    %---------------------------------------------------------
    \cventry
    {Operational security officer} % Position
    {Société Générale} % Company
    {Paris, France} % Location
    {Jan. 2009 - Jul. 2011} % Date(s)
    { % Description
    Being a member of the operational security team transversal to servers, backup, storage and database subjects, I worked on several cross-technologies projects as a developer, project manager and tech leader. \hfill\break
    Some main projects were: \hfill\break
        \begin{cvitems}
            \item {Create automate to collect accesses on various systems and link them to people identity (IAM) / KSH, PERL, PHP, SSH /}
            \item {Automate installation and configuration of IDS sensors for massive deployment over the network / Snort, KSH, SSH /}
            \item {Web interface for security KPIs / PHP, MySQL, IIS /}
            \item {Tool to follow security patches deployment and application regarding internal process (compliance) based on an ETL and a web front-end layers. / PHP, MySQL, MSSQL /}
            \item {Define and implement an internal X.509 PKI to enroll dynamically AD domain computers / OpenSSL, X.509v3, Python /}
            \item {Front-end to submit certification requests (either from a CSR or from scratch) with secured generation and transmission of private parts / PHP, Python, X.509v3, OpenSSL, MySQL /}
            \item {SIEM integration to collect, store, normalize and correlate logs from various sources (IDS, systems, DB, …) to raise pertinent security alerts / PERL, Intellitactics, Red Hat EL, Regular Expressions /}
        \end{cvitems} \hfill\break
        \begin{cvskills}
            \cvskill {Technical context} {Windows Server, Red Hat EL, DB, …}
        \end{cvskills}
    }
    %---------------------------------------------------------

    %---------------------------------------------------------
    \cventry
    {Operational security consultant} % Position
    {ON-X} % Company
    {Paris, France} % Location
    {Sept. 2006 - Dec. 2008} % Date(s)
    { % Description
        \begin{cvitems}
            \item {Sign certification requests with internal PKI CA}
            \item {Maintain tools}
            \item {Deploy security « bastions » over EMEA offices to secure a server in case of viral crisis}
            \item {Deploy data collection scripts on servers over US and APAC sites and train co-workers}
        \end{cvitems}
    }
    %---------------------------------------------------------

    %---------------------------------------------------------
    \cventry
    {Operational security developer} % Position
    {ON-X} % Company
    {Paris, France} % Location
    {Sept. 2006 - Dec. 2008} % Date(s)
    { % Description
        Final internship for master degree in an operational security team. \hfill\break
        In charge of some tools development such as: \hfill\break
        \begin{cvitems}
            \item {Patch management reporting on Unix \& Windows systems}
            \item {NIS password change intranet}
            \item {Password strength tester tool}
            \item {User accesses collect tool}
        \end{cvitems} \hfill\break
        \begin{cvskills}
            \cvskill {Technical context} {PHP, Perl, Apache, HTML4, CSS2, Javascript, MySQL, SMS}
        \end{cvskills}
    }
    %---------------------------------------------------------

    %---------------------------------------------------------
    \cventry
    {Web developer} % Position
    {Malinea (Cashstore)} % Company
    {Paris, France} % Location
    {Apr. 2005 - Aug. 2005} % Date(s)
    { % Description
        Web-developer trainee for a cash-back application. \hfill\break
        Front-end development, massive mail distribution and customer database maintenance. \hfill\break
        \begin{cvskills}
            \cvskill {Technical context} {ASP.NET, HTML4, CSS2, Javascript, MSSQL}
        \end{cvskills}
    }
    %---------------------------------------------------------

    %---------------------------------------------------------
    \cventry
    {Webmaster} % Position
    {Atomik} % Company
    {Paris, France} % Location
    {Aug. 2004 - Apr. 2006} % Date(s)
    { % Description
        Official website and eShop webmaster for a Paintball company.
        \begin{cvskills}
            \cvskill {Technical context} {PHP, HTML4, CSS2, MySQL, Javascript}
        \end{cvskills}
    }
    %---------------------------------------------------------
\end{cventries}